MLH1 Results Outline

### 2020-03-04 doc/MatMeth.Rmd
note to self
notes for results, more work on Methods

---
title: "Material Methods"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_MatMeth.bib
---

@@

>>>>

---
title: "Material Methods"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
    toc_depth: '5'
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
bibliography: refs_MatMeth.bib
---

@@

Todo

Add the single Bivalent predictions to one of the sections.

### 2020-03-04 doc/Results.rmd
notes for results, more work on Methods

@@

In M1, the model build on the mouse averages of IFD^norm^ metrics with subspecies and strain as fixed effects, the high recombining strains had significant strain effects for (glm; p = `r sum.Q2.M1glm_IFD.PER$coefficients[,4][6]`, p = `r sum.Q2.M1glm_IFD.PER$coefficients[,4][7]` and p = `r sum.Q2.M1glm_IFD.PER$coefficients[,4][8]` for _musculus^PWD^_, _molossinus^MSM^_ and _musculus^SKIVE^_, respectively). 
In the M2 model results, _musculus^PWD^_, and _musculus^SKIVE^_, were the only significant strain effects, (glm; p = `r sum.Q2.M2glm_IFD.PER$coefficients[,4][4]` and p = `r sum.Q2.M2glm_IFD.PER$coefficients[,4][7]`).
Running M2 within subspecies – confirms the within subepcies predictions across strains – (no significant strain effects 
Q2.glm.M2_IFD.PER_Dom
Q2.glm.M2_IFD.PER_Musc
Q2.glm.M2_IFD.PER_Mol -->
<!--

>>>>

nrm.IFD_MOLF_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MOLF" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_PER, x= fileName, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS MOLF")+facet_wrap(~mouse, scales = "free")+ylim(c(0,1))+theme(axis.text.x = element_blank())

raw.IFD_MOLF_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MOLF" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_ABS, x= mouse, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS MOLF")+theme(axis.text.x = element_blank())+ylim(c(0, 100))

raw.IFD_MSM_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MSM" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = IFD1_ABS, x= mouse, color=chromosomeLength))+geom_point()+ggtitle("Interfocal Distances, ABS MSM")+theme(axis.text.x = element_blank())+ylim(c(0, 100))

Fby.F.IFD_MOLF_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MOLF" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = Foci1, x=Foci2, color=chromosomeLength))+geom_point()+ggtitle("FOce Pos by Fos Pos MOLF")+facet_wrap(~mouse, scales = "free")+ylim(c(0,75))+xlim(c(0,120))+theme(legend.position="none")

Fby.F.IFD_MSM_BIV.data <- ggplot( (Curated_BivData %>% filter(strain =="MSM" ) %>%  filter(hand.foci.count == "2") %>%  filter(sex == "male")  ) , aes(y = Foci1, x=Foci2, color=chromosomeLength))+geom_point()+ggtitle("Foci Pos by Fos Pos MSM")+facet_wrap(~mouse, scales = "free")+ylim(c(0,75))+xlim(c(0,120))+theme(legend.position="none")

@@

In M1, the model build on the mouse averages of IFD^norm^ metrics with subspecies and strain as fixed effects, the high recombining strains had significant strain effects for (glm; p = `r sum.Q2.M1glm_IFD.PER$coefficients[,4][6]`, p = `r sum.Q2.M1glm_IFD.PER$coefficients[,4][7]` and p = `r sum.Q2.M1glm_IFD.PER$coefficients[,4][8]` for _musculus^PWD^_, _molossinus^MSM^_ and _musculus^SKIVE^_, respectively). 
In the M2 model results, _musculus^PWD^_, and _musculus^SKIVE^_, were the only significant strain effects, (glm; p = `r sum.Q2.M2glm_IFD.PER$coefficients[,4][4]` and p = `r sum.Q2.M2glm_IFD.PER$coefficients[,4][7]`).
Running M2 within subspecies confirms the within subepcies predictions across strains – (no significant strain effects 
Q2.glm.M2_IFD.PER_Dom
Q2.glm.M2_IFD.PER_Musc
Q2.glm.M2_IFD.PER_Mol -->
<!--
